Monitoring Time Series With Missing Values:\\a Deep Probabilistic Approach

### 2022-02-17 paper.tex
cosmetic

A popular realization of the forecasting model
$\mathcal{M}_\theta$ is a recurrent neural network (RNN), with
$\theta$ corresponding to the network parameters.  There is a
range of neural recurrent models of varying complexity to deal
with time series forecasting. Most models include a recurrent
unit which threads the state through the time steps, accepts
data as inputs and produces next step predictions as outputs.
The simplest model is an RNN with a fully-connected readout
layer to produce forecasts
(Figure~\ref{fig:dt-conventional-model}).  RNN can be based on
LSTM~\cite{}, GRU~\cite{}, or another architectural variant, and
is often multi-layer.  Architectures  may also include
intermediate modules and sampling-based variational
layers~\cite{}. The overall architecture stays almost the same,
with more connections, intermediate modules and sampling-based
variational layers.

@@

However, the basic scheme outlined above poses difficulty in
applications with high-dimensional time series and partially
missing observations. Sampling based uncertainty assertion
impacts performance, and missing observations are often imputed
in \textit{ad hoc} manner~\cite{}. An architecture which
incorporates confidence about data and in which observed and
predicted data are interchangeable is  highly desirable. For
example, if out of 5 components 3 were measured and 2 predicted
from an earlier step we want to input them both into the next
time step for further forecasting. In addition, the model
architecture should be capable of robust uncertainty prediction
and benefit from training with multiple steps of out-of-sample
data.

>>>>

A popular realization of the forecasting model
$\mathcal{M}_\theta$ is a recurrent neural network (RNN), with
$\theta$ corresponding to the network parameters.  There is a
range of neural recurrent models of varying complexity to deal
with time series forecasting. Most models include a recurrent
unit which threads the state through the time steps, accepts
data as inputs and produces next step predictions as outputs.
The simplest model is an RNN with a fully-connected readout
layer to produce forecasts
(Figure~\ref{fig:dt-conventional-model}).  RNN can be based on
LSTM~\cite{HS97}, GRU~\cite{CMB+14}, or another architectural variant, and
is often multi-layer.  Architectures  may also include
intermediate modules and sampling-based variational
layers~\cite{CKD+15,YB21}. The overall architecture stays almost
the same, with more connections, intermediate modules and
sampling-based variational layers.

@@

However, the basic scheme outlined above poses difficulty in
applications with high-dimensional time series and partially
missing observations. Sampling based uncertainty assertion
impacts performance, and missing observations are often imputed
heuristically~\cite{LKW16,SYG+19}. An architecture which
incorporates confidence about data and in which observed and
predicted data are interchangeable is  highly desirable. For
example, if out of 5 components 3 were measured and 2 predicted
from an earlier step we want to input them both into the next
time step for further forecasting. In addition, the model
architecture should be capable of robust uncertainty prediction
and benefit from training with multiple steps of out-of-sample
data.
